error checking the LE decomp functions

### 2016-10-25 Code/error checking the LE decomp fxs.Rmd

```{r compare decomp_output}
round(cbind(age_decomp$C_x, age_decomp2$C_x),4)
```

@@

@@

life.table(data = cali.complete, age.groups = "ages", num.ages.in.group = "nx", 
           death.counts = "obs.deaths", population.counts = "obs.popn")

@@

life.table(data = cali.complete, age.groups = "ages", num.ages.in.group = "nx", ave.prop.lived = "avelived",
           death.counts = "obs.deaths", population.counts = "obs.popn")
```

@@

library(dplyr)
cali.abridged <- cali.complete %>% group_by(group) %>% 
                                   summarise(nx = sum(nx), ages = first(group), popn = sum(obs.popn), deaths = sum(obs.deaths),
                                             avelived = first(avelived))

@@

data.frame(life.table(data = cali.abridged, age.groups = "ages", num.ages.in.group = "nx", 
           death.counts = "deaths", population.counts = "popn"))

data.frame(life.table(data = cali.abridged, age.groups = "ages", num.ages.in.group = "nx", 
           death.counts = "deaths", population.counts = "popn", ave.prop.lived = "avelived"))
```

>>>>

```{r compare_decomp_output}
round(cbind(age_decomp$C_x, age_decomp2$C_x),4)
```

@@

Collapse by age and confirm these line up with the marginal age decomposition:
```{r }
age.contribution <- canada.cod.decomp %>% group_by(Ages) %>% summarise(age.contribution = sum(C_xi))

age.contribution
```

@@

life.table(data = cali.complete, num.ages.in.group = "nx", 
           death.counts = "obs.deaths", population.counts = "obs.popn")

@@

life.table(data = cali.complete, num.ages.in.group = "nx", ave.prop.lived = "avelived",
           death.counts = "obs.deaths", population.counts = "obs.popn")
```

@@

cali.abridged <- cali.complete %>% group_by(group) %>% 
                                   summarise(nx = sum(nx), ages = first(group), popn = sum(obs.popn), deaths = sum(obs.deaths),
                                             avelived = first(avelived))

@@

data.frame(life.table(data = cali.abridged, num.ages.in.group = "nx", 
           death.counts = "deaths", population.counts = "popn"))

data.frame(life.table(data = cali.abridged, num.ages.in.group = "nx", 
           death.counts = "deaths", population.counts = "popn", ave.prop.lived = "avelived"))
```
